---
title: "Neurofeedback Amygdala activation analysis"
author: "Or Duek"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: yes
---

# Analysis of clinical data

```{r, message=FALSE, results='hide'}
# load libraries
require(tidyverse)
require(lme4)
require(lmerTest)
require(ggplot2)
```
```{r, message=FALSE, results='hide'}
# load dataset
clincal_df <- read_csv('CAPS_bcde_clusters_1019.csv')
clincal_df$X14 <- NULL
clincal_df$X8 <- NULL

# make it long (create a function for easier use)
names_long_reexp <- c('b_total_screening', 'b_total_30d', 'b_total_60d')
names_long_hyper <- c('e_total_screening', 'e_total_30d','e_total_60d')
names_long_total <- c('CAPS_total_screening', 'CAPS_total_30d', 'CAPS_total_60d')
clincal_df_longTotal <- pivot_longer(select(clincal_df, "Subject ID","Neurofeedback Intervention", names_long_total), cols = names_long_total, names_to = 'time', values_to = 'score') %>% rename("subject" = "Subject ID", "group"="Neurofeedback Intervention")
clincal_df_longTotal$time <- factor(clincal_df_longTotal$time, levels=c("CAPS_total_screening", "CAPS_total_30d", "CAPS_total_60d"))

clincal_df_longReexp <- pivot_longer(select(clincal_df, "Subject ID","Neurofeedback Intervention", names_long_reexp), cols = names_long_reexp, names_to = 'time', values_to = 'score') %>% rename("subject" = "Subject ID", "group"="Neurofeedback Intervention") 
clincal_df_longReexp$time <- factor(clincal_df_longReexp$time, levels = names_long_reexp)

clincal_df_longHyper <- pivot_longer(select(clincal_df, "Subject ID","Neurofeedback Intervention", names_long_hyper), cols = names_long_hyper, names_to = 'time', values_to = 'score') %>% rename("subject" = "Subject ID", "group"="Neurofeedback Intervention")
clincal_df_longHyper$time <- factor(clincal_df_longHyper$time, levels = names_long_hyper)
```
## Descriptives

```{r}
MASS::truehist(clincal_df$CAPS_total_screening)
```

# Mixed effect models


## Plot the scores
```{r}
ggplot(clincal_df_longTotal, aes(x=time, y=score, color=group)) + geom_boxplot() + theme_minimal() + ggtitle("Total CAPS")
ggplot(clincal_df_longReexp, aes(x=time, y=score, color=group)) + geom_boxplot() + theme_minimal() + ggtitle("Reexperiencing")
ggplot(clincal_df_longHyper, aes(x=time, y=score, color=group)) + geom_boxplot() + theme_minimal() + ggtitle("HyperArousal")
```

## Run the models

### Total Scores
```{r}
model1 <- lmer(score ~ time * group + (1|subject), data=clincal_df_longTotal)
summary(model1)
anova(model1)

ggplot(clincal_df_longTotal, aes(x=group, y=score, color=time)) + geom_boxplot() + theme_minimal() + ggtitle("Total CAPS")
```

There is a significant difference between the timepoint (people improve), but no significant difference between the groups nor interaction. It is worth noticing that being in the Sham group adds 6 points to the total score, with all other predictors having negative influence on the score.

### Reexperiencing

```{r}
model2 <- lmer(score ~ time * group + (1|subject), data=clincal_df_longReexp)
summary(model2)
anova(model2)
ggplot(clincal_df_longReexp, aes(x=group, y=score, color=time)) + geom_boxplot() + theme_minimal() + ggtitle("Reexperiencing")
```

We can also see here, effect for time with no other thing. Here the differences between groups are even smaller.

### Hyperarousal

```{r}
model3 <- lmer(score ~ time * group + (1|subject), data=clincal_df_longHyper)
summary(model3)
anova(model3)
ggplot(clincal_df_longHyper, aes(x=group, y=score, color=time)) + geom_boxplot() + theme_minimal() + ggtitle("HyperArousal")
```

Same thing.


