---
title: "Neurofeedback Amygdala activation analysis"
author: "Or Duek"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: yes
---

# Loading and organizing data

```{r, results='hide', message=FALSE}
# loading libraries
library(lme4)
library(lmerTest)
library(tidyverse)
library(emmeans)
```


```{r, warning=FALSE, results='hide'}
# loading and organizing data
df <- read.csv('roi_data_regulation_untrained.csv')
dfReal <- select(df, Subject, Group, Pre.untrained, Post_untrained, FU_untrained)
df_long <- pivot_longer(dfReal, cols = c('Pre.untrained', 'Post_untrained', 'FU_untrained'))
# change names for easier interpretation
colnames(df_long) <- c('subject','group','time','value')
df_long$time <- factor(df_long$time, levels = c('Pre.untrained','Post_untrained','FU_untrained'))
df_long$group <- factor(df_long$group, levels = c('Real','Sham'))
```

# Statistical models
## Mixed level model with subjects nested within group
```{r}
# random intercept
model1 <- lmer(value ~ time * group + (1|subject), data= df_long)
summary(model1)
anova(model1)
BIC(model1)
```

```{r}

library(ggplot2)
ggplot(df_long, aes(x=group, y=value, color=time)) + geom_boxplot() + theme_minimal()# + geom_line()

```

## Using baseline as covariate

```{r}
## After talking with Tobias - leave baseline also in the time variable
df_long_baseline <- pivot_longer(dfReal, cols = c('Pre.untrained','Post_untrained', 'FU_untrained'))
df_long_baseline <- merge(df_long_baseline, dfReal[,c('Subject','Pre.untrained')]) # adding the baseline
colnames(df_long_baseline) <- c('subject','group','time','value','baseline')

df_long_baseline$time <- factor(df_long_baseline$time, levels = c('Pre.untrained','Post_untrained','FU_untrained'))
df_long_baseline$group <- factor(df_long_baseline$group, levels = c('Real','Sham'))
# remove NAs from the baseline
#df_long_baseline <- df_long_baseline[!is.na(df_long_baseline$baseline), ]

model4 <- lmer(value ~ time * group + baseline + (1|subject), data=df_long_baseline)
summary(model4)
anova(model4)
```

```{r}
VarCorr(model4) # total sigma 0.3
emm <- emmeans(model4,  ~group, by='time')

emmip(model4, group ~ time, CIs = T) + theme_minimal()
eff_size(emm, sigma = 0.3, edf = 2)
```

So, it seems we have an effect size of 0.34 after treatment but 1.088 at follow-up. 
Lets plot the change from baseline of each group

### Comparing time effect sized
```{r}
emm2 <- emmeans(model4,  ~time, by='group')
eff_size(emm2, sigma = 0.3, edf = 2)
```
So here we have an effect of >0.7 for both after trt and follow-up in the real group. 

## Graph of difference from baseline

```{r, warning=FALSE, results='hide'}
dfGraph <- df
dfGraph$delta0 <- 0
dfGraph$delta1 <- dfGraph$Post_untrained - dfGraph$Pre.untrained
dfGraph$delta2 <- dfGraph$FU_untrained - dfGraph$Pre.untrained
dfGraph_long <- pivot_longer(dfGraph, cols = c('delta0','delta1','delta2'), names_to = 'time')
```
 


```{r, warning=FALSE}
ggplot(dfGraph_long, aes(x=time, y=value, color=Group, group=Group)) + geom_smooth(level = 0.68) + theme_minimal()
```

We have used standard error of the mean hear, to make it clearer.

## Calculate partial eta square

```{r}
library(sjstats)
am2 <- anova_stats(model4)
am2
```

